Rust for Operating System Development: A Systematic Literature Review

### 2024-04-17 paper.tex
Updated RQ

\begin{itemize}
    \item \textbf{RQ1:} What are the existing approaches, methodologies, and best practices for
      implementing operating system kernels in Rust?
    \item \textbf{RQ2:} What are the performance implications of using Rust for operating system
      kernel development in terms of throughput, latency, and resource utilization?
    \item \textbf{RQ3:} What are the major challenges and limitations encountered when developing
      operating system kernels in Rust, particularly in comparison to other languages?
\end{itemize}

>>>>

\begin{itemize}
    \item \textbf{RQ1:} What are the existing approaches and methodologies for implementing
      operating system kernels in Rust?
    \item \textbf{RQ2:} What are the performance implications of using Rust for operating system
      kernel development in terms of throughput, latency, and resource utilization?
    \item \textbf{RQ3:} What are the major challenges and limitations encountered when developing
      operating system kernels in Rust, particularly in comparison to other languages?
    \item \textbf{RQ4:} What are the best practices for implementing operating system kernels in Rust?
\end{itemize}
